% !TEX encoding = IsoLatin
\begin{center}
{\large \textit{Abstract} }
\end{center}
%\newenvironment{resumo_ingles}
%{\thispagestyle{empty} \vspace*{\stretch{1}}\begin{flushleft} \em}{\end{flushleft} \vspace*{\stretch{3}}}






%{\centering \large
%{\large\bf \textbf{Abstract} } }

\vspace{0.5cm}
\quad Nowadays there is a great ease in accessing information and widespread interest in using  this information to increase the comfort and welfare of people. Knowledge is recognized as a powerful weapon that tends to be exploited to the limit. Thus matter find all the sources of information that may be helpful to achieve this global goal. In this sense, the potential of environment information surrounding a human being is huge and the lack of exploitation that occurs on that knowledge is a fault that should be corrected. Given this perspective there are several ways of applying this knowledge, including the ability to provide better living conditions and welfare. The aim of this work is to develop an architecture composed by sensors placed in a distributed way, capable of monitoring intelligent environments based on several factors. In this architecture the function of each sensor can be viewed as a service to its users, being collected through them different types of information. This work, through the several indicators collected, offers its users access to diverse information about their behaviour and reactions during  the monitoring period.
\vspace{3cm}

\textbf{Key Words:} Architecture, Services, Ambient Intelligence, Monitoring, Sensors.